Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_3_model.tex
Fix RoBERTa mixing section

\subsubsection{Mixing RoBERTa layers}
RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
embeddings, $\bG_i \in \mathbb{R}^{2048 \times S}$ for $i \in \{0,1,
2,...,24\}$. This includes the initial uncontextualized embeddings and the
output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum across
all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bX_T &=& \sum_{i=0}^{24} \alpha_i \bG_i
\end{IEEEeqnarray*}
where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $\alpha_i$ are learnable weights.

>>>>

\subsubsection{Mixing RoBERTa layers}
RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
embeddings, $\bG = \{\bg_{\ell i} \in \mathbb{R}^{2048} : i \in \{1, 2,...,
49\}, \ell \in \{ 0, 1,..., 24 \}\}$. This includes the initial
uncontextualized embeddings and the output of each of the 24 layers. Inspired
by Tenney \etal \cite{Tenney2019BertRT}, who showed that different layers in
BERT represent different steps in the traditional NLP pipeline, we take a
weighted sum across all layers to obtain the article embedding $\bx_{Ti}$:
\begin{IEEEeqnarray*}{lCl}
   \bx_{Ti} &=& \sum_{\ell=0}^{24} \alpha_\ell \, \bg_{\ell i}
\end{IEEEeqnarray*}
where  $\alpha_\ell$ are learnable weights.
